### 2017-06-05 Objects/Objects.tex
Corrections

%\subsection{Isolation}
%\label{sec:objects_ele_iso}
The identification requirements discussed up to now reduce the backgrounds 
from misidentified electrons, but do not eliminate them completely. If jets are
misidentified as electrons, or an electron resulting from a heavy-flavour 
decay is identified, the electron is not isolated. Therefore requirements
on the electron isolation can reduce these backgrounds even further.
Different isolation definitions are used in \ac{CMS}. The default, which is
used for the analyses presented in later chapters, is a combined relative isolation variable
defined as \cite{SMHtautauCMS}:
\begin{equation}\label{eqn:electron_reliso}
I_{\text{rel}} = \frac{\Sigma p_{\text{T}}^{\text{charged}} + \mathrm{max}(\Sigma E_{\text{T}}^{\text{neutral}} + \Sigma E_{\text{T}}^{\text{photon}} - \Delta\beta \Sigma E_{\text{T}}^{\text{PU}},0)}{p_{\text{T}}^{e}},
\end{equation}
where the \pT~and \ET~sums are taken within a cone in $\eta$-$\phi$ around the direction
of the electron of size $\Delta R = 0.4$ during Run 1 and $\Delta R = 0.3$ during Run 2 \cite{CMS-PAS-HIG-16-037}.
The sum over \pT$^{\text{charged}}$ corresponds to the \pT~of all charged %\ac{PF} 
hadrons associated with the primary vertex. %and within the cone of radius $\Delta R$ around
%the electron's axis. 
The \ET$^{\text{neutral}}$ and \ET$^{\text{photon}}$ sums
run over all neutral hadronic energy and photon energy. %within the cone of radius $\Delta R$.
The contribution from neutral particles due to pileup needs to be subtracted from
the sum of these two terms. It is estimated as the sum of charged hadronic \pT~for hadrons not associated
with the primary vertex, multiplied by a $\Delta \beta$ factor of $\frac{1}{2}$.

@@

In the \Htohhtobbtautau analysis, where Run 1 data 
was used, muons were required to pass ``tight'' identification requirements \cite{cms-muon-reco}. 
In addition to having to be reconstructed by the global muon algorithm, selections
are made on the $\chi^2$ per degrees of freedom of the track fit, number of hits of the inner
track in different tracker layers and number of muon segments the inner track is matched to.
%TIGHT REQUIREMENTS
%\begin{itemize}
%\setlength{\itemsep}{-\baselineskip}
%\item The muon must be reconstructed by the global muon algorithm
%\item The $\chi^2$/$N_{\text{dof}}$ of the global track fit must be smaller than 10
%\item The global track fit must include hits from at least one chamber in the muon system
%\item The inner tracker track must be matched to muon segments in at least two muon stations (which means the muon must also be reconstructed as a tracker muon)
%\item The tracker track must have at least one hit in the pixel detector, and hits in ten tracker layers.
%\end{itemize}

@@

The particles identified by the \ac{PF} algorithm
are clustered into jets using the anti-\kT~algorithm \cite{antiKT} as implemented
in \texttt{FastJet} version 3.0.1 \cite{fastjet}. Jet clustering algorithms 
define distance parameters $d_{ij}$, denoting the distance between object (particle or cluster of 
particles) $i$ and 
object $j$, and $d_{iB}$ denoting the distance between 
object $i$ and the beam. The smallest of these distances
is determined and if this is a distance between an object i and an object j, objects
i and j are combined. If the smallest distance is a $d_{iB}$, object i
is called a jet and removed from the list of objects. In the anti-\kT~algorithm
these distance parameters are defined as:
\begin{align}\label{eqn:objects_antikt}
d_{ij}=\text{min}(p_{\text{T},i}^{-2},p_{\text{T},j}^{-2})\frac{\Delta_{ij}^2}{R^2}\notag\\
d_{iB} = p_{\text{T}}^{-2},
\end{align}
where $\Delta_{ij} = \sqrt{(y_i-y_j)^2+(\phi_i - \phi_j)^2}$ is the distance
between the objects i and j in rapidity-azimuthal angle space. The radius
parameter $R$ was chosen as 0.5 during Run~1 \cite{cms-jec-2011} and as 0.4 during Run~2 \cite{cms-jets-run2}. 
This algorithm is collinear- and infrared-safe, which means that the number of jets
is not affected by the emission of soft collinear gluons or parton splitting.
To reject badly reconstructed jets and fake jets due to noise, clustered jets are required to 
pass loose identification requirements \cite{cms-jet-algos-run1,cms-jets-run2}. These requirements are based on the 
charged and neutral particle multiplicities in the jet, as well as on the fraction
of jet energy carried by different \ac{PF} particle types.

@@

%\subsection{Isolation and discrimination against light leptons}
%\label{sec:objects_tau_iso}
Requiring the reconstructed \Pgth to be isolated reduces the $\text{jet}\rightarrow\Pgth$ fake rate. Isolation
discriminators can be defined using the isolation sum,
\begin{equation}\label{eqn:cutbased_iso}
I_{\Pgt} = \Sigma p_{\text{T}}^{\text{charged}}(d_Z < 0.2\text{ cm}) + \text{max}(0,\Sigma p_{\text{T}}^{\Pphoton} - \Delta \beta \Sigma p_{\text{T}}^{\text{charged}} (d_Z > 0.2 \text{ cm}) ),
\end{equation}
where the first term denotes the sum of the transverse momenta of all charged particles not part
of the identified \Pgth. Only particles with \pT~$> 0.5\,\GeV$ within a cone of $\Delta R = 0.5$ centred around the 
direction of the \Pgth are taken into account and the charged particle tracks are required to be compatible with having
originated from the \Pgth production vertex. This is achieved by requiring the longitudinal impact parameter
with respect to the primary vertex to be $d_z < 0.2\,\cm$. The second term of equation \ref{eqn:cutbased_iso} denotes the sum
of the transverse momenta of photons with $\pTm > 0.5$ GeV within a cone of $\Delta R = 0.5$ centred around the direction
of the \Pgth. The effect of pileup on this term is accounted for by subtracting the sum of the momenta of charged
particles with \pT~$> 0.5\,\GeV$, within a cone of $\Delta R = 0.8$ around the direction of the hadronic tau and
tracks not compatible with having originated from the production vertex of the hadronic tau, multiplied by
a $\Delta \beta$ factor of 0.2.%FIXME rephrase

In addition to the isolation sum, a requirement on the sum of transverse momenta
of electrons and photons included in strips but which are located outside of the signal cone,
\begin{equation}\label{eqn:ptouter_iso}
p_{\text{T}}^{\text{strip, outer}} = \Sigma p_{\text{T}}^{\Pe/\Pphoton}(\Delta R > R_{\text{sig}}) < 0.10\cdot p_{\text{T}}^{\Pgt},
\end{equation}
can be made.
An MVA \Pgth isolation discriminator combines isolation variables with tau lifetime information into a \ac{BDT} to discriminate between \Pgth decays and quark and gluon jets.
Some of the variables used as input are:
\begin{itemize}
\setlength{\itemsep}{-0.5\baselineskip}
\item Isolation sums, including those in equations \ref{eqn:cutbased_iso} and \ref{eqn:ptouter_iso}.
\item Track-related variables such as impact parameters, quality of the track, and information about decay vertices.
\item Information about photons: the momentum-weighted $\Delta R$, $\Delta \eta$ and $\Delta \phi$ of photons in strips inside or outside the signal cone, in addition to the number of signal and isolation photons found.
\item \Pgth-related kinematic quantities, plus the reconstructed decay mode.  
%\item The charged-and neutral-particle isolation sums
%\item The reconstructed $\tau_{h}$ decay mode
%\item The transverse impact parameter $d_{xy}$ of the leading track of the $\tau_{h}$ candidate with the vertex, and its significance $d_{xy}/\sigma_{d_{xy}}$, and its sign (the projection of the impact parameter vector on the $\tau_h$ direction)
%\item The 3-dimensional impact parameter $d_{xyz}$ of the leading track, and it significance
%\item The distance between the $\tau$ production and decay vertices, its significance, and information about whether a decay vertex has successfully been reconstructed for a given candidate.
%\item $p_{\text{T}}$ and $\eta$ of the $\tau_{h}$ candidate
%\item $\Delta \beta$ corrected isolation (as equation \ref{eqn:cutbased_iso}
%\item The sum of transverse momenta of electrons and photons included in strips but located outside of the signal cone (equation \ref{eqn:ptouter_iso})
%\item The $\chi^2$ value of the fit for the leading track of the $\tau_{h}$ candidate
%\item The ratio of the total electromagnetic energy to the total energy within the $\tau_h$ signal cone.
%\item The total number of signal and isolation photons with $p_{\text{T}} > 0.5$~GeV
%\item The $p_{\text{T}}$ weighted $\Delta R$ of photons within signal cone and the isolation annulus
%\item The $p_{\text{T}}$ weighted $\Delta \eta$ and $\Delta \phi$ of photons in strips outside of the signal cone.
\end{itemize}

@@

In order to reduce the $\Pe\rightarrow\Pgth$ and $\Pgm\rightarrow\Pgth$ fake rates, 
anti-electron and anti-muon discriminators are used. 
The anti-electron discriminator is a \ac{BDT}-based discriminator trained using input variables such as:
\begin{itemize}
\setlength{\itemsep}{-0.5\baselineskip}
\item Kinematic variables of the \Pgth candidate and \ac{GSF} track, including visible mass of the \Pgth.
\item Energy and momentum ratios such as the fraction of electromagnetic energy, \ac{ECAL} and \ac{HCAL} energy relative to track momentum.
\item Photon-related variables, such as the momentum-weighted $\Delta \eta$ and $\Delta \phi$ between photons, the fraction of the \Pgth energy carried by photons, and the number of photons found in strips.
\item Information on the quality of the track.
%\item \pT, $\eta$ of the $\Pgt_{h}$ candidate
%\item \pT, $\eta$, $\sigma_{p_{\text{T}}}/p_{\text{T}}$ of the \ac{GSF} track
%\item Distance in $\eta$ and $\phi$ of the \ac{GSF} track to the nearest boundary between \ac{ECAL} modules.
%\item Electromagnetic energy fraction $E_{\text{ECAL}}/(E_{\text{ECAL}}+E_{\text{HCAL}})$
%\item Ratio of \ac{ECAL} and \ac{HCAL} energy fractions relative to the momentum of the leading charged track
%\item The \pT weighted RMS distances in $\eta$ and $\phi$ between the photons in any strip and the leading 
%charged track (calculated separately for photons inside and outside the $\Pgt$ signal cone)
%\item The fraction of $\Pgt_{h}$ energy carried by photons (calculated separately for photons inside and outside the $\Pgt_h$ signal cone)
%\item $(p_{in} - p_{out})/p_{in}$
%\item The number of photons in any of the strips associated with the $\Pgt_h$ candidate, calculated separately for photons inside and outside the $\Pgt_h$ signal cone
%\item The ratio between the total \ac{ECAL} energy and inner track momentum
%\item The ratio of energies of bremsstrahlung photons measured in the \ac{ECAL} and the tracker
%\item The visible mass of the $\Pgt_h$ candidate, for photons and charged particles within the $\Pgt_h$ signal cone
%\item $\chi^2/Ndof$ of the GSF track fit
%\item $N_{hits}^{GSF}-N_{hits}^{KF}/N_{hits}^{GSF}+N_{hits}^{KF}$, With $N_{hits}^{GSF}$ the number of hits associated with the track in the \ac{GSF} track reconstruction algorithm, and
%similarly $N_{hits}^{KF}$ for the \ac{KF} track reconstruction algorithm.
\end{itemize}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[Isolation performance]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyIsol.pdf}}\\
\subfloat[Real \Pgth efficiency for anti-\Pe discriminator]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyEle.pdf}}
\subfloat[$\Pe\rightarrow$\Pgth fake rate for the anti-\Pe discriminator]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauMisIDEle.pdf}}
\end{center}
\caption[Figures of the jet$\rightarrow$\Pgth fake rate in simulated QCD events
versus $\Pgth$ identification efficiency for simulated $\PHiggs\rightarrow\Pgt\Pgt$ events, the real
$\Pgth$ identification efficiency for different working points of the anti-electron discriminator, and the \mbox{$\Pe\rightarrow\Pgth$} fake rate for different
working points of the anti-electron discriminator.]{(a) The jet$\rightarrow$\Pgth fake rate in simulated QCD multijet events versus \Pgth identification
efficiency for simulated $\PHiggs\rightarrow\Pgt\Pgt$ events, comparing the MVA-based isolation discriminator in red with the cut-based 
isolation discriminator in pink. Tighter working points give lower hadronic tau identification
efficiencies and lower fake rates, and for the same \Pgth identification efficiency the fake rate
from the MVA-based discriminator is lower than from the cut-based discriminator. (b) The real \Pgth identification
efficiency for different working points of the anti-electron discriminator as a function of the \pT~of the \Pgth, and (c)
the $\Pe\rightarrow$\Pgth fake rate for different working points of the anti-electron discriminator, as a function of
the \pT~of the electron \cite{cms-tau-2015}.}
\label{fig:tau_efficiency}
\end{figure}
The anti-muon discriminator is a cut-based discriminant, for which a loose and a tight working
point are provided. It is based on variables such as the number of track segments found in various
parts of the muon system around the direction of the \Pgth, and comparisons of calorimeter energy
with the momentum of the leading \Pgth track.
%\begin{itemize}
%\setlength{\itemsep}{-\baselineskip}
%\item \textbf{Loose:} The $\Pgt_h$ candidate is vetoed by this discriminator if track segments are found in at least two muon stations within a cone of $\Delta R = 0.3$ of the $\Pgt_h$ direction, or if the sum of the electromagnetic and hadronic energy ($E_{\text{ECAL}}+E_{\text{HCAL}}$) is smaller than $0.2\cdot p_{\text{leading track}}$.
%Otherwise it passes the discriminator.
%\item \textbf{Tight:} The $\Pgt_h$ candidate passes this working point if it passes the loose working point and no hits are present within a cone of $\Delta R=0.3$ of the $\Pgt_h$ direction in the \ac{CSCs},\ac{RPCs} and \ac{DT} in the two outermost muon stations.
%\end{itemize}

>>>>

%\subsection{Isolation}
%\label{sec:objects_ele_iso}
The identification requirements discussed up to now reduce the backgrounds 
from misidentified electrons, but do not eliminate them completely. If jets are
misidentified as electrons, or an electron resulting from a heavy-flavour 
decay is identified, the electron is not isolated. Therefore requirements
on the electron isolation can reduce these backgrounds even further.
Different isolation definitions are used in \ac{CMS}. The default, which is
used for the analyses presented in later chapters, is a combined relative isolation variable
defined as \cite{SMHtautauCMS}:
\begin{equation}\label{eqn:electron_reliso}
I_{\text{rel}} = \frac{\Sigma p_{\text{T}}^{\text{charged}} + \mathrm{max}(\Sigma E_{\text{T}}^{\text{neutral}} + \Sigma E_{\text{T}}^{\text{photon}} - \Delta\beta \Sigma E_{\text{T}}^{\text{PU}},0)}{p_{\text{T}}^{e}},
\end{equation}
where the \pT~and \ET~sums are taken within a cone in $\eta$-$\phi$ around the direction
of the electron of size $\Delta R = 0.4$ during Run 1 and $\Delta R = 0.3$ during Run 2 \cite{CMS-PAS-HIG-16-037}.
The sum over \pT$^{\text{charged}}$ corresponds to the \pT~of all charged %\ac{PF} 
hadrons associated with the primary vertex. %and within the cone of radius $\Delta R$ around
%the electron's axis. 
The \ET$^{\text{neutral}}$ and \ET$^{\text{photon}}$ sums
run over all neutral hadronic energy and photon energy. %within the cone of radius $\Delta R$.
The contribution from neutral particles due to pileup needs to be subtracted from
the sum of these two terms. It is estimated as the sum of charged hadronic \pT~for hadrons not associated
with the primary vertex, multiplied by a $\Delta \beta$ factor of $\frac{1}{2}$. This factor
is the average ratio of neutral to charged particles, which is measured in jets 
by studying the fraction of energy carried by charged and neutral constituents \cite{cms-pf-2010-2}.

@@

In the \Htohhtobbtautau analysis, where Run 1 data 
were used, muons were required to pass ``tight'' identification requirements \cite{cms-muon-reco}. 
In addition to having to be reconstructed by the global muon algorithm, selections
are made on the $\chi^2$ per degrees of freedom of the track fit, number of hits of the inner
track in different tracker layers and number of muon segments the inner track is matched to.
%TIGHT REQUIREMENTS
%\begin{itemize}
%\setlength{\itemsep}{-\baselineskip}
%\item The muon must be reconstructed by the global muon algorithm
%\item The $\chi^2$/$N_{\text{dof}}$ of the global track fit must be smaller than 10
%\item The global track fit must include hits from at least one chamber in the muon system
%\item The inner tracker track must be matched to muon segments in at least two muon stations (which means the muon must also be reconstructed as a tracker muon)
%\item The tracker track must have at least one hit in the pixel detector, and hits in ten tracker layers.
%\end{itemize}

@@

The particles identified by the \ac{PF} algorithm
are clustered into jets using the anti-\kT~algorithm \cite{antiKT} as implemented
in \texttt{FastJet} version 3.0.1 \cite{fastjet}. Jet clustering algorithms 
define distance parameters $d_{ij}$, denoting the distance between object (particle or cluster of 
particles) $i$ and 
object $j$, and $d_{iB}$ denoting the distance between 
object $i$ and the beam. The smallest of these distances
is determined and if this is a distance between an object $i$ and an object $j$, objects
$i$ and $j$ are combined. If the smallest distance is a $d_{iB}$, object $i$
is called a jet and removed from the list of objects. In the anti-\kT~algorithm
these distance parameters are defined as:
\begin{align}\label{eqn:objects_antikt}
d_{ij}=\text{min}(p_{\text{T},i}^{-2},p_{\text{T},j}^{-2})\frac{\Delta_{ij}^2}{R^2}\notag\\
d_{iB} = p_{\text{T}}^{-2},
\end{align}
where $\Delta_{ij} = \sqrt{(y_i-y_j)^2+(\phi_i - \phi_j)^2}$ is the distance
between the objects $i$ and $j$ in rapidity-azimuthal angle space. The radius
parameter $R$ was chosen as 0.5 during Run~1 \cite{cms-jec-2011} and as 0.4 during Run~2 \cite{cms-jets-run2}. 
This algorithm is collinear- and infrared-safe, which means that the number of jets
is not affected by the emission of soft collinear gluons or parton splitting.
To reject badly reconstructed jets and fake jets due to noise, clustered jets are required to 
pass loose identification requirements \cite{cms-jet-algos-run1,cms-jets-run2}. These requirements are based on the 
charged and neutral particle multiplicities in the jet, as well as on the fraction
of jet energy carried by different \ac{PF} particle types.

@@

The three prong + 1 \Ppizero decay mode, which would reconstruct the 
\Ptaupm $\rightarrow$ h$^{\pm}$h$^{\mp}$h$^{\pm}$\Ppizero\Pnut decay, 
suffers from large contamination by jets and is therefore not considered.

%\subsection{Isolation and discrimination against light leptons}
%\label{sec:objects_tau_iso}
Requiring the reconstructed \Pgth to be isolated reduces the $\text{jet}\rightarrow\Pgth$ fake rate. Isolation
discriminators can be defined using the isolation sum,
\begin{equation}\label{eqn:cutbased_iso}
I_{\Pgt} = \Sigma p_{\text{T}}^{\text{charged}}(d_Z < 0.2\text{ cm}) + \text{max}(0,\Sigma p_{\text{T}}^{\Pphoton} - \Delta \beta \Sigma p_{\text{T}}^{\text{charged}} (d_Z > 0.2 \text{ cm}) ),
\end{equation}
where the first term denotes the sum of the transverse momenta of all charged particles not part
of the identified \Pgth. Only particles with \pT~$> 0.5\,\GeV$ within a cone of $\Delta R = 0.5$ centred around the 
direction of the \Pgth are taken into account and the charged particle tracks are required to be compatible with having
originated from the \Pgth production vertex. This is achieved by requiring the longitudinal impact parameter
with respect to the primary vertex to be $d_z < 0.2\,\cm$. The second term of equation \ref{eqn:cutbased_iso} denotes the sum
of the transverse momenta of photons with $\pTm > 0.5$ GeV within a cone of $\Delta R = 0.5$ centred around the direction
of the \Pgth. The effect of pileup on this term is accounted for by subtracting the sum of the momenta of charged
particles with \pT~$> 0.5\,\GeV$, within a cone of $\Delta R = 0.8$ around the direction of the hadronic tau and
tracks not compatible with having originated from the production vertex of the hadronic tau, multiplied by
a $\Delta \beta$ factor of 0.2. This factor accounts for the fraction of neutral to charged energy. To determine 
it, the photon energy sum discussed above is fitted as a function of the quantity $\Sigma p_{\text{T}}^{\text{charged}} (d_Z > 0.2 \text{ cm})$.
The slope of this linear fit is taken as the $\Delta \beta$ factor.

In addition to the isolation sum, a requirement on the sum of transverse momenta
of electrons and photons included in strips but which are located outside of the signal cone,
\begin{equation}\label{eqn:ptouter_iso}
p_{\text{T}}^{\text{strip, outer}} = \Sigma p_{\text{T}}^{\Pe/\Pphoton}(\Delta R > R_{\text{sig}}) < 0.10\cdot p_{\text{T}}^{\Pgt},
\end{equation}
can be made.
An MVA \Pgth isolation discriminator combines isolation variables with tau lifetime information into a \ac{BDT} to discriminate between \Pgth decays and quark and gluon jets.
The variables used as inputs are:
\begin{itemize}
\setlength{\itemsep}{-0.5\baselineskip}
\item Isolation sums of charged and neutral particles, in addition to the isolation sums in equations \ref{eqn:cutbased_iso} and \ref{eqn:ptouter_iso}.
\item Track-related variables: the impact parameters, quality of the track, information about decay vertices.
\item Information about photons: the momentum-weighted $\Delta R$, $\Delta \eta$ and $\Delta \phi$ of photons in strips inside or outside the signal cone, in addition to the number of signal and isolation photons found.
\item \Pgth-related variables: the reconstructed decay mode and \Pgth kinematics.  
\item The ratio of the total electromagnetic energy to the total energy within the \Pgth signal cone.
%\item The charged-and neutral-particle isolation sums
%\item The reconstructed $\tau_{h}$ decay mode
%\item The transverse impact parameter $d_{xy}$ of the leading track of the $\tau_{h}$ candidate with the vertex, and its significance $d_{xy}/\sigma_{d_{xy}}$, and its sign (the projection of the impact parameter vector on the $\tau_h$ direction)
%\item The 3-dimensional impact parameter $d_{xyz}$ of the leading track, and it significance
%\item The distance between the $\tau$ production and decay vertices, its significance, and information about whether a decay vertex has successfully been reconstructed for a given candidate.
%\item $p_{\text{T}}$ and $\eta$ of the $\tau_{h}$ candidate
%\item $\Delta \beta$ corrected isolation (as equation \ref{eqn:cutbased_iso}
%\item The sum of transverse momenta of electrons and photons included in strips but located outside of the signal cone (equation \ref{eqn:ptouter_iso})
%\item The $\chi^2$ value of the fit for the leading track of the $\tau_{h}$ candidate
%\item The ratio of the total electromagnetic energy to the total energy within the $\tau_h$ signal cone.
%\item The total number of signal and isolation photons with $p_{\text{T}} > 0.5$~GeV
%\item The $p_{\text{T}}$ weighted $\Delta R$ of photons within signal cone and the isolation annulus
%\item The $p_{\text{T}}$ weighted $\Delta \eta$ and $\Delta \phi$ of photons in strips outside of the signal cone.
\end{itemize}

@@

In order to reduce the $\Pe\rightarrow\Pgth$ and $\Pgm\rightarrow\Pgth$ fake rates, 
anti-electron and anti-muon discriminators are used. 
The anti-electron discriminator is a \ac{BDT}-based discriminator trained using the following input variables:
\begin{itemize}
\setlength{\itemsep}{-0.5\baselineskip}
\item Kinematic variables of the \Pgth candidate and the \ac{GSF} track, plus the visible mass of the \Pgth candidate.
\item Energy and momentum ratios: the fraction of electromagnetic energy, plus the \ac{ECAL} and \ac{HCAL} energy relative to track momentum.
\item Photon-related variables: the momentum-weighted $\Delta \eta$ and $\Delta \phi$ between photons, the fraction of the \Pgth energy carried by photons, the ratio of
the energies of bremsstrahlung photons measured in the \ac{ECAL} and the tracker, and the number of photons found in strips.
\item Information on the quality of the track.
%\item Distance in $\eta$ and $\phi$ of the \ac{GSF} track to the nearest boundary between \ac{ECAL} modules.
%\item $(p_{in} - p_{out})/p_{in}$
%\item $\chi^2/Ndof$ of the GSF track fit
%\item $N_{hits}^{GSF}-N_{hits}^{KF}/N_{hits}^{GSF}+N_{hits}^{KF}$, With $N_{hits}^{GSF}$ the number of hits associated with the track in the \ac{GSF} track reconstruction algorithm, and
%similarly $N_{hits}^{KF}$ for the \ac{KF} track reconstruction algorithm.
%\item \pT, $\eta$ of the $\Pgt_{h}$ candidate
%\item \pT, $\eta$, $\sigma_{p_{\text{T}}}/p_{\text{T}}$ of the \ac{GSF} track
%\item Electromagnetic energy fraction $E_{\text{ECAL}}/(E_{\text{ECAL}}+E_{\text{HCAL}})$
%\item The ratio between the total \ac{ECAL} energy and inner track momentum
%\item Ratio of \ac{ECAL} and \ac{HCAL} energy fractions relative to the momentum of the leading charged track
%\item The \pT weighted RMS distances in $\eta$ and $\phi$ between the photons in any strip and the leading 
%charged track (calculated separately for photons inside and outside the $\Pgt$ signal cone)
%\item The fraction of $\Pgt_{h}$ energy carried by photons (calculated separately for photons inside and outside the $\Pgt_h$ signal cone)
%\item The ratio of energies of bremsstrahlung photons measured in the \ac{ECAL} and the tracker
%\item The visible mass of the $\Pgt_h$ candidate, for photons and charged particles within the $\Pgt_h$ signal cone
%\item The number of photons in any of the strips associated with the $\Pgt_h$ candidate, calculated separately for photons inside and outside the $\Pgt_h$ signal cone
\end{itemize}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[Isolation performance]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyIsol.png}}\\
\subfloat[Real \Pgth efficiency for anti-\Pe discriminator]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyEle.pdf}}
\subfloat[$\Pe\rightarrow$\Pgth fake rate for the anti-\Pe discriminator]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauMisIDEle.pdf}}
\end{center}
\caption[Figures of the jet$\rightarrow$\Pgth fake rate in simulated QCD events
versus $\Pgth$ identification efficiency for simulated $\PHiggs\rightarrow\Pgt\Pgt$ events, the 
$\Pgth$ identification efficiency for different working points of the anti-electron discriminator, and the \mbox{$\Pe\rightarrow\Pgth$} fake rate for different
working points of the anti-electron discriminator.]{(a) The jet$\rightarrow$\Pgth fake rate in simulated QCD multijet events versus \Pgth identification
efficiency for simulated $\PHiggs\rightarrow\Pgt\Pgt$ events, comparing the MVA-based isolation discriminator in red with the cut-based 
isolation discriminator in pink. Tighter working points give lower hadronic tau identification
efficiencies and lower fake rates, and for the same \Pgth identification efficiency the fake rate
from the MVA-based discriminator is lower than from the cut-based discriminator. Figure adapted from \cite{cms-tau-2015}. (b) The \Pgth identification
efficiency in simulated \Ztautau events for different working points of the anti-electron discriminator as a function of the \pT~of the \Pgth, and (c)
the $\Pe\rightarrow$\Pgth fake rate in simulated \Zee events for different working points of the anti-electron discriminator, as a function of
the \pT~of the electron \cite{cms-tau-2015}. Note that the efficiencies and fake rates are fully derived from simulation and serve to give
an indication of the efficiencies of the different working points relative to each other.}
\label{fig:tau_efficiency}
\end{figure}
The anti-muon discriminator is a cut-based discriminant, for which a loose and a tight working
point are provided. It is based on variables such as the number of track segments found in various
parts of the muon system around the direction of the \Pgth, and comparisons of calorimeter energy
with the momentum of the leading \Pgth track.
%\begin{itemize}
%\setlength{\itemsep}{-\baselineskip}
%\item \textbf{Loose:} The $\Pgt_h$ candidate is vetoed by this discriminator if track segments are found in at least two muon stations within a cone of $\Delta R = 0.3$ of the $\Pgt_h$ direction, or if the sum of the electromagnetic and hadronic energy ($E_{\text{ECAL}}+E_{\text{HCAL}}$) is smaller than $0.2\cdot p_{\text{leading track}}$.
%Otherwise it passes the discriminator.
%\item \textbf{Tight:} The $\Pgt_h$ candidate passes this working point if it passes the loose working point and no hits are present within a cone of $\Delta R=0.3$ of the $\Pgt_h$ direction in the \ac{CSCs},\ac{RPCs} and \ac{DT} in the two outermost muon stations.
%\end{itemize}

### 2017-06-05 Theory/Theory.tex
Corrections

\section{Beyond the standard model}
\label{sec:theory_BSM}
The \ac{SM} has been successfully tested to high accuracy \cite{pdg-2014}. However,
some issues remain that cannot be addressed by the \ac{SM} alone \cite{griffiths}.
For example, it does not provide a candidate for dark matter, which is estimated
to make up 25\% of the matter-energy density in the universe.
In addition, the running coupling constants of the electroweak and
strong forces do not intersect at a common energy scale. Another problem is that the force
of gravity does not appear in the \ac{SM}.

These points aside, the most important issue concerning
the Higgs sector of the \ac{SM} is the hierarchy problem.
The \ac{SM}
is accepted to be an effective field theory that describes
the elementary particles and their interactions well, up to an energy scale $\Lambda$ beyond which it breaks down.
This is the energy scale at which new physics must enter.
It is known that $\Lambda \leq \mathcal{O}(10^{19})$, the Planck scale, as quantum 
gravitational effects start to become important in that region. The energy scale $\Lambda$ enters
the corrections due to fermion and boson loops to the Higgs boson mass quadratically \cite{MSSM-carena-haber}:
\begin{equation}\label{eqn:mh_hierarchy}
\begin{split}
&M_{\PHiggs_{\text{SM}}}^2  = (M_{\PHiggs})_0^2 + \Delta M_{\PHiggs}^2,\\
&\Delta M_{\PHiggs}^2 \sim \mathcal{O}(\Lambda^2).
\end{split}
\end{equation}
Thus assuming that there is no new physics all the way up to
the Planck scale the observation $M_{\PHiggs}=125\,\GeV$ would only be compatible with $\Lambda$ of order $10^{19}\,\GeV$
if there was extreme fine-tuning of the bare Higgs boson mass $(M_{\PHiggs})_0^2$.

>>>>

\section{Beyond the standard model}
\label{sec:theory_BSM}
The \ac{SM} has been successfully tested to high accuracy \cite{pdg-2014}. However,
some issues remain that cannot be addressed by the \ac{SM} alone.
For example, it does not provide a candidate for dark matter, which is estimated
to make up 25\% of the matter-energy density in the universe \cite{Bertone:2004pz}.
In addition, the running coupling constants of the electroweak and
strong forces do not intersect at a common energy scale \cite{GUT-LEP}. Another problem is that the force
of gravity does not appear in the \ac{SM} \cite{Carlip:2001wq}.

These points aside, the most important issue concerning
the Higgs sector of the \ac{SM} is the hierarchy problem \cite{SUSY-primer}.
The \ac{SM}
is accepted to be an effective field theory that describes
the elementary particles and their interactions well, up to an energy scale $\Lambda$ beyond which it breaks down.
This is the energy scale at which new physics must enter.
It is known that $\Lambda \leq \mathcal{O}(10^{19})$, the Planck scale, as quantum 
gravitational effects start to become important in that region. The energy scale $\Lambda$ enters
the corrections due to fermion and boson loops to the Higgs boson mass quadratically \cite{MSSM-carena-haber}:
\begin{equation}\label{eqn:mh_hierarchy}
\begin{split}
&M_{\PHiggs_{\text{SM}}}^2  = (M_{\PHiggs})_0^2 + \Delta M_{\PHiggs}^2,\\
&\Delta M_{\PHiggs}^2 \sim \mathcal{O}(\Lambda^2).
\end{split}
\end{equation}
Thus, assuming that there is no new physics all the way up to
the Planck scale, the observation $M_{\PHiggs}=125\,\GeV$ would only be compatible with $\Lambda$ of order $10^{19}\,\GeV$
if there was extreme fine-tuning of the bare Higgs boson mass $(M_{\PHiggs})_0^2$.
